Quantum Hoare Type Theory

### 2020-11-06 ms-paper/ms-paper.tex
Add definition of span

>>>>

\todo{Consider defining orthomodular lattices}

Let us define the notation and basic definitions we will need for talking about subspaces of a Hilbert space.

\begin{definition}[Span of a subspace]
	For any subspace $X$ in a Hilbert space $\mathcal{H}$, written ($X \subseteq \mathcal{H}$), $\mathit{span}(X)$ is the smallest closed subspace of $\mathcal{H}$ containing $X$. In other words, $\mathit{span}(X)$ is the set of linear combinations of vectors in $X$.
\end{definition}

Further, $S(\mathcal{H})$ is the set of closed subspaces of $\mathcal{H}$. If we write $\mathcal{P(H)}$ for the set of all quantum predicates on $\mathcal{H}$, then $S(\mathcal{H}) \subseteq \mathcal{P(H)}$.

Now we can define the logical operations on quantum predicates:
